%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Merchandiser} % Job title
{PepsiCo.} % Organization
{Kitchener, ON} % Location
{May. 2021 - Aug. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for product merchandising within large volume stores. Built customer relationships at store level.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Cashier} % Job title
{the Beer Store} % Organization
{Cambridge, ON} % Location
{Jun. 2019 - Aug. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Consistently provided exceptional customer service and support to management.}
\item {Proactively identified and resolved issues with customer complaints and equipment.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Concessions Cashier} % Job title
{Landmark Cinemas} % Organization
{Cambridge, ON} % Location
{May. 2018 - Jun. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Processed and balanced financial transactions accurately within operating procedures.}
\item {Helped build a positive, diverse, and fun work environment by promoting team effectiveness.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Sales Assistant} % Job title
{Galt Chrysler DOdge Jeep RAM} % Organization
{Cambridge, ON} % Location
{Jun. 2017 - Sep. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {• Coordinated activities to support sales team productivity and customer relationship management accountabilities}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{ShitOne Corp. (Start-up company)} % Organization
{Seoul, S.Korea} % Location
{Dec. 2011 - Feb. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Freelance Penetration Tester} % Job title
{SAMSUNG Electronics} % Organization
{S.Korea} % Location
{Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
\item {Conducted penetration testing on SAMSUNG Smart TV.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}