%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Javascript, Node.JS, HTML, CSS, Firebase, Express} % Languages
{BattleBoat.JS} % Title
{}
{}
{ % Description(s)
\begin{cvitems}
\item {An update to an existing JavaScript and CSS version of the popular board game Battleship where a player would face off against an AI. The updated version of the game included various improvements and additional features. New functionality included account sign-up and login with Firebase backend that held user information and player performance statistics, allowing for ship rearranging after placement before the game starts, and a new headquarters game mode (a 1x1 square is randomly placed on the gird and causes instant loss if hit)}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Ruby, Ruby on Rails} % Languages
{Nine Men's Morris} % Title
{}
{}
{ % Description(s)
\begin{cvitems}
\item {A version of the board game of the same name written in Ruby. Matchmaking would be completed with a player creating a room and giving the joining player the room code. Once both players successfully join the lobby, either player can start the game. During the game, each player can see the board and the board updates live for both players as they continue to make moves.}
\end{cvitems}
}

\cventry
{Java} % Languages
{Rogue Game} % Title
{}
{}
{ % Description(s)
\begin{cvitems}
\item {A simple game written in Java that allows players to move around room to room and collect various items. Includes UI to display the game screen, inventory, the players name and name changing field.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}